taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-02-28 paper/manuscript.Rmd
WIP on manuscript

```{r}
syn <- unmatched$input %>% synonyms("iucn")
syn
```

Three of these synonyms are considered accepted names in OTT:

@@

```{r}
syn$synonym %>% na.omit() %>% get_ids("ott")
syn %>% na.omit() %>% mutate(
  #ott = get_ids(synonym, "ott"),
                             col = get_ids(synonym, "col"),
                             itis = get_ids(synonym, "itis"),
                             gbif = get_ids(synonym, "gbif"))
```

syns <- unmatched$input %>% ids("iucn") %>%
        dplyr::filter(taxonomicStatus != "accepted") %>%
        dplyr::select(synonym = scientificName,
                      synonym_id = taxonID,
                      taxonomicStatus,
                      acceptedNameUsageID)
accepted

syn <- unmatched$input %>% synonyms("iucn")
syn
```

>>>>

Of the remaining 10 names, 3 are clearly common names (`gull`, `tern`, `woodpecker`), two (`trochilid` and `ardeid`) are references to family names, *Trochilidae* and *Ardeidae*, and the remaining five are unresolved.  Let us attempt to resolve these five before we consider the cases of common names and family names.

Consulting IUCN Redlist names, we can resolve acceptedNameUsageIDs for four of these five:

```{r}
unmatched %>% mutate(iucn = get_ids(input, "iucn", "prefix"))
```

By consulting the synonyms table, we can see what other names these species might be known by:

```{r}
syn <- unmatched$input %>% synonyms("iucn")
```

```{r}
x <- syn %>% 
  mutate(ott_id = get_ids(synonym, "ott", "prefix")) %>% 
  select(input, ott_id) %>%
  na.omit()

syn$synonym %>% get_ids("ott", "prefix")

descendants(id = x$ott_id, provider = "ott") %>% select(scientificName, taxonomicStatus, acceptedNameUsageID)
```

```{r}
x
```

Note that three of the four synonyms given by IUCN are considered accepted names in OTT:

@@

We can look for these synonyms in other tables too. ITIS recognizes some of these unmatched names as synonyms and some as accepted names.

```{r}
unmatched$input %>% synonyms("itis")

unmatched$input %>% ids("itis")

## 
syn$synonym %>% na.omit() %>% unique() %>% synonyms("itis")

We can confirm the family names can be resolved:

```{r}
c("Trochilidae",  "Ardeidae") %>% ids("ott")
```

We can use the common names table to resolve common names:
